Verifying Demonstrations

### 2018-05-27 paper/LocationProofs.tex
coincoin

Some \ac{LBS} only grant access to resources to users located at a particular 
location,  thus raising the issue of verifying the position claimed by a 
particular user. In most current schemes, the location of a user/device is 
determined by the device itself (\eg through GPS) and forwarded to the \ac{LBS} 
provider. One of the main drawback of this approach is that a user can cheat by 
having his device transmitting a false location. Therefore, it is possible for a 
user to be inappropriately granted access to a particular resource while being 
thousands of kilometers away.

To counter this threat, \iac{LBS} should ask the requesting device to formally 
prove that it really is at the claimed location. This notion can be formalized 
through the concept of \emph{location proof}. In a nutshell, a location proof is 
a digital certificate attesting that someone was at a particular location at a 
specific moment in time. A location proof architecture is a system by which 
users can obtain location proofs from neighboring witnesses (\eg trusted access 
points or other users) that can later be shown to verifiers who can check the 
validity of a particular proof. Most of the existing approaches to location 
proofs require the prover and the witnesses to disclose their identities, thus 
raising many privacy issues such as the possibility of tracing the movements of 
users of the location proof architecture.
\seb{to do add the corresponding reference}
However, some location proofs systems, such as \ac{PROPS}, exists that provides 
strong privacy guarantees along with the possibility of verifying the claim of 
the location. \PRIVO share some similarities with \ac{PROPS}, although their 
objective is quite different as we aim at verifying a global property of the 
population (\ie crowd estimation) in contrast to checking the location claim 
made by a user, which is an individual property.

>>>>

Some LBS only grant access to resources to users located at a particular location, thus raising the issue of verifying the position claimed by a particular user. 
In most of the existing schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the LBS provider. 
One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.

One possible way to counter this threat is by having the requesting device formally proven that it really is at the claimed location, which give rise to the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof. 
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus 
raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
\seb{to do add the corresponding reference}
However, some location proofs systems, such as PROPS, exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
\PRIVO share some similarities with PROPS, although their objective is quite different as we aim at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.

### 2018-05-27 paper/TimeStamp.tex
coincoin

\NewCryptoScheme{\TS}{TS}
\NewAlgorithm{\TSget}{\TS.\!Get}
\NewAlgorithm{\TSstamp}{\TS.\!Stamp}
\NewAlgorithm{\TSverify}{\TS.\!Verify}
\NewAlgorithm{\TStime}{\TS.\!Time}

@@

We can instantiate \(\TS\) using a blockchain, \eg OmniLedger~\cite{OmniLedger}.
The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and return the block into which \(x\) was included.
\(\TSget\) will return the hash of the current head of the chain.
This value is difficult to predict since it depends on all submitted transactions and usually some randomness (\eg nonces and miners' secrets).
The blockchain must also be continuously extended, such as in Bitcoin~\cite{Bitcoin}, in which a new block appears approximately every 10 minutes.
Having a dedicated blockchain for a protest will not do, and thus it is better to use a blockchain which is also used for other things too.

There are some additional properties that we need from \(\TS\), which are implied by blockchains.
First, we need \emph{immutability}, to ensure that once we commit something (through \(\TSstamp\)) it will remain there.
We will use this to ensure verifiability as the data must remain to be verifiable.
Second, once we have committed some data, we do not need to keep the data itself, but we can store some confirmation value instead.
For instance using blockchains, we can store the hash of the block in which our data was committed, while this block remains we are sure that our data remains committed --- even if we no longer remember what our data looked like.
We will use this property to approximate the property of receipt freeness.

>>>>

%\NewScheme{\TS}{TS}
\NewAlgorithm{\TSget}{\TS.\!Get}
\NewAlgorithm{\TSstamp}{\TS.\!Stamp}
\NewAlgorithm{\TSverify}{\TS.\!Verify}
\NewAlgorithm{\TStime}{\TS.\!Time}

@@

We can instantiate \(\TS\) using a blockchain, \eg OmniLedger~\cite{OmniLedger}.
The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and 
return the identifier of the block into which \(x\) was included.
\(\TSget\) will return the hash of the current head of the chain.
This value is difficult to predict since it depends on all submitted transactions and usually some randomness (\eg nonces and miners' secrets).
The blockchain must also be continuously extended, such as in Bitcoin~\cite{Bitcoin}, in which a new block appears approximately every 10 minutes.
Having a dedicated blockchain for a protest will not do, and thus it is better 
to use a blockchain which is used for other things too.

There are some additional properties that we need from \(\TS\), which are implied by blockchains.
First, we need \emph{immutability}, to ensure that once we commit something (through \(\TSstamp\)) it will remain there.
We will use this to ensure verifiability as the data must remain to be verifiable.
Second, once we have committed some data, we do not need to keep the data itself, but we can store some confirmation value instead.
For instance using blockchains, we can store the hash of the block in which our 
data was committed, while this block remains we are sure that our data remains 
committed --- even if we no longer remember what our data looked like.
